Zohmg---a large scale data store for aggregated time-series-based data. [DRAFT]

### 2009-05-07 doc/report/msc-report.tex
doc/report/msc-report.tex: * fixed underscores so tex source compiles.

The actual parsing of the log is abstracted; it is the emitting of dimensionality data I want to showcase in this example. We assume that parse_apache_log() accepts a single line from the log file and returns an object with the appropriate fields, such as useragent ant statuscode.

>>>>

The actual parsing of the log is abstracted; it is the emitting of
dimensionality data I want to showcase in this example. We assume that
parse\_apache\_log() accepts a single line from the log file and returns an
object with the appropriate fields, such as useragent ant statuscode.
